---
title: "Simulate time series"
author: "Wanda De Keersmaecker"
date: ""
output: rmarkdown::html_vignette
vignette: >
%\VignetteIndexEntry{Simulate time series}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  ---
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

```{r, include=FALSE}
# source_rmd <- function(file, local = FALSE, ...){
#   options(knitr.duplicate.label = 'allow')
#   
#   tempR <- tempfile(tmpdir = ".", fileext = ".R")
#   on.exit(unlink(tempR))
#   knitr::purl(file, output=tempR, quiet = TRUE)
#   
#   envir <- globalenv()
#   source(tempR, local = envir, ...)
# }
```

## Inputs
* ifolder: directory to folder where the data characteristics are stored
* ofolder: directory to folder where the simulated time series will be stored
* basename: base name of the data files

```{r}
ifolder <- 'C:\\Users\\keers001\\OneDrive\ -\ WageningenUR\\RETURN\\Data\\RETURN\\20191019_SimulationOptSAR\\Landsat\\SimTS\\'#'../Data/' #'C:\\Users\\keers001\\OneDrive\ -\ WageningenUR\\RETURN\\Data\\RETURN\\20191019_SimulationOptSAR\\Landsat\\Test_TSrequired\\TS_10\\SimTS\\'  # folder with data characteristics
ofolder <- 'C:\\Users\\keers001\\OneDrive\ -\ WageningenUR\\RETURN\\Data\\RETURN\\20191019_SimulationOptSAR\\Landsat\\SimTS\\'#'../Data/' # 'C:\\Users\\keers001\\OneDrive\ -\ WageningenUR\\RETURN\\Data\\RETURN\\20191019_SimulationOptSAR\\Landsat\\Test_TSrequired\\TS_10\\SimTS\\'  # folder where the simulated time series will be saved

basename <- 'LSTS_RndmSample_NoFire_5_Tree_80_scl_30_npnt_20000_VI'# 'toyset' # 'LSTS_RndmSample_NoFire_5_Tree_80_scl_30_npnt_20000_VI'# base name of the data files
```

## Import data and source functions

```{r}
library(BenchmarkRecovery)
  library(zoo)
# source( '../R/fun_general.R')
# source( '../R/fun_simulate.R')
# import settings file
sttngs <- loadRData(file = file.path(ifolder, paste0(basename, '_simTS_settings_var.rda')))

```

## Simulate time series

```{r}
# iterate over parameters that are evaluated
for(vr in 1:length(sttngs$variables)){#length(sttngs$variables) c(4,7)
  # initiale lists to store the simulated time series 
  simTS <- list()
  simTSTr <- list()
  simTSSeas <- list()
  simTSRem <- list()
  # simTSDist <- list()
  simTSParam <- list()
  
  #setvr <- sttngs[[vr]]# settings of simulation
  evr <- sttngs$variables[vr]# name of parameter that will be evaluated in the simulation
  
  # iterate over values of evaluated parameter and simulate nrep time series per combination of all other variables
  for (i in 1:length(sttngs[[evr]])){     
    # print(i)
    # define all possible combination of the values of the parameters (except the one to be evaluated)
    vrit <- sttngs$variables[-vr] # parameters that should be combined
    comb <- expand.grid(sttngs[vrit]) # combine all parameters, except the evaluated one
    comb[[evr]] <- sttngs[[evr]][i] # add value of parameter to be evaluated
    
    # initiate a list to store the simulated time series for this particular parameter
    simTSi <- list()
    simTSTri <- list()
    simTSSeasi <- list()
    simTSRemi <- list()
    # simTSDisti <- list()
    simTSParami <- list()
    
    # iterate over the parameter combinations and simulate each time nrep time series per parameter combination
    cnt <- 0
    for (pari in 1: dim(comb)[1]){
      # simulate nrep time series for a parameter combination
      sc <- simulCase(sttngs$nrep, comb$nyr[pari], sttngs$nobsYr, sttngs$nDr, sttngs$seasAv, comb$seasAmp[pari],
                      sttngs$trAv, comb$remSd[pari], c(comb$distMag[pari],comb$distMag[pari]), 
                      comb$distT[pari], c(comb$distRec[pari],comb$distRec[pari]), sttngs$remcoef, 
                      comb$missVal[pari], sttngs$DistMissVal, sttngs$distType)
      # compress each of the simulated time series and store the time series in a list 
      for (parii in 1:sttngs$nrep){
        cnt <- cnt+1
        simTSi[[cnt]] <- TScompress(sc[[1]][parii,])
        simTSTri[[cnt]] <- sc[[2]][parii,1]
        tmp <-sc[[3]][parii,]
        tmp[is.na(sc[[1]])] <- NA
        simTSSeasi[[cnt]] <- TScompress(tmp)
        tmp <-sc[[4]][parii,]
        tmp[is.na(sc[[1]])] <- NA
        simTSRemi[[cnt]] <- TScompress(tmp)
        # simTSDisti[[cnt]] <- sc[[5]][parii,]
        simTSParami[[cnt]] <- sc[[6]][parii,]
      }            
      rm(sc)
    } 
    
    simTS[[i]] <- simTSi
    simTSTr[[i]] <- simTSTri
    simTSSeas[[i]] <- simTSSeasi
    simTSRem[[i]] <- simTSRemi
    # simTSDist[[i]] <- simTSDisti
    simTSParam[[i]] <- simTSParami
    rm(comb, simTSi, simTSTri, simTSSeasi, simTSRemi, simTSParami)#, simTSDisti
    gc()
  }   
  save(simTS, file = file.path(ofolder, paste0(basename, '_simTS_' , evr, '.rda')))# '_', i,
  save(simTSTr, file = file.path(ofolder, paste0(basename, '_simTSTr_', evr, '.rda')))
  save(simTSSeas, file = file.path(ofolder, paste0(basename, '_simTSSeas_', evr, '.rda')))
  save(simTSRem, file = file.path(ofolder, paste0(basename, '_simTSRem_', evr, '.rda')))
  # save(simTSDist, file = file.path(ofolder, paste0(basename, '_simTSDist_', evr, '.rda')))
  save(simTSParam, file = file.path(ofolder, paste0(basename, '_simTSParam_', evr, '.rda')))
  rm(simTS,simTSTr,simTSSeas, simTSRem, simTSParam) #simTSDist
  # gc()
}
```
## plot example of simulated series

```{r}
evar <- 'missVal'#'distMag''nyr', 'seasAmp','remSd','distMag','distT', 'distRec', 'missVal'
load(file.path(ofolder, paste0(basename, '_simTS_',evar,'.rda')))# '_', i,
load(file.path(ofolder, paste0(basename, '_simTSTr_',evar,'.rda')))
load(file.path(ofolder, paste0(basename, '_simTSSeas_',evar,'.rda')))
load(file.path(ofolder, paste0(basename, '_simTSRem_',evar,'.rda')))
load(file.path(ofolder, paste0(basename, '_simTSParam_',evar,'.rda')))

```
```{r}
ii <- 1
for (i in 1:length(simTSParam)){
  tm <- 1:(simTSParam[[i]][[ii]]$number_yrs * simTSParam[[i]][[ii]]$obs_per_year)
  dt <- as.Date('2000-01-01') + tm
  
  if(simTSParam[[i]][[ii]]$dist_type == 'exponential'){
    simDist <- exponential(tm, pert = simTSParam[[i]][[ii]]$dist_magn, tpert = simTSParam[[i]][[ii]]$dist_time, thalf = simTSParam[[i]][[ii]]$dist_rec)
  }
  if(simTSParam[[i]][[ii]]$dist_type == 'piecewise'){
    simDist <- piecewise(tm, pert = simTSParam[[i]][[ii]]$dist_magn, tpert = simTSParam[[i]][[ii]]$dist_time, thalf = simTSParam[[i]][[ii]]$dist_rec)
  }
  
  seas <- simTSTr[[i]][[ii]]+TSdecompress(simTSSeas[[i]][[ii]])
  tsi <- TSdecompress(simTS[[i]][[ii]])
  
  plot(zoo(tsi[is.na(tsi)==F],dt[is.na(tsi)==F]),type = 'o', xlab = 'Time', ylab = 'VI',
       main = paste0('n = ', simTSParam[[i]][[ii]]$number_yrs, ', A = ', round(simTSParam[[i]][[ii]]$seas_amp, digits = 3), ', sd = ', round(simTSParam[[i]][[ii]]$rem_sd, digits = 3), ', Dm = ', round(simTSParam[[i]][[ii]]$dist_magn, digits = 3), ', Dt = ', round(simTSParam[[i]][[ii]]$dist_time/simTSParam[[i]][[ii]]$obs_per_year, digits = 1), ', Dr = ', round(simTSParam[[i]][[ii]]$dist_rec/simTSParam[[i]][[ii]]$obs_per_year, digits = 3), ', ', strtrim(simTSParam[[i]][[ii]]$dist_type,3),', mv = ', round(simTSParam[[i]][[ii]]$miss_val,digits = 3)  ))
  lines(zoo(simTSTr[[1]][[1]]+simDist,dt), col = 'red', lw = 2)
  lines(zoo(seas[is.na(seas)==F],dt[is.na(seas)==F]), col = 'darkcyan', lw = 2)
  
  
}




```
